Pareto-Optimal Multistate Protein Design using Tree Graphical Models

### 2013-01-06 docs/tex/experiments.tex
Wrote method for calculating base frequencies
Designed tied experiment for zif268. Experiment failed with slope>0. Can't imagine why

>>>>

We use all the sequences and secondary structures of SCOP fold of the protein under consideration. For 1HTM it is the 'Stalk segment of viral fusion proteins' fold. For 1AAY it is 'beta-beta-alpha zinc fingers' fold. 
While training the HMM we deduplicate all sequence, sec. structure pairs. All X and U amino acids are not considered. We add a 5\% bias to all background to match background frequencies. This is done by : 
\[
P(O=a|X=b) = \frac{Count(O=a,X=b)+Count(O=a)\times 0.05}{Count(X=b)+Count(O)\times 0.05}
\]
